Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-08-07 Ben_Manuscripts/Paper1/results.tex
Update results.tex

@@

We varied the relative interlayer orientation between sandwiched and 
parallel-displaced based on our knowledge of the stability of these two
pi-stacking modes. Short simulations were run with position restraints
on benzene rings. Simulated X-ray diffraction patterns generated from 
each configuration establishes a link between the parallel displaced 
stacking mode and major features present in experimental XRD patterns.  % FIGURE!!!!!!!!!!
The faint ring at a distance of $\approx$ 1.5 \angstrom \textsuperscript{-1} 
is commonly identified as a result of the average packing distance 
between alkane chains. Four spots of higher intensity are visible in the 
alkane chain region creating an x-shaped pattern. The spots are only
generated for structures created in the parallel displaced configuration.
In the past, the spots have been attributed to the tilt angle of the 
alkane chains. Theoretically the angle is the same as that made between 
the spots and the x-axis. However, we achieved the same pattern with 
a calculated average tilt angle of 0 $\pm$ 9 degrees. % GET THE RIGHT NUMBER !!!!!

>>>>

% Paragraph describing the experimental 2D WAXS Pattern

@@

We varied the relative interlayer orientation between sandwiched and 
parallel-displaced based on our knowledge of the stability of these two
pi-stacking modes. Short NVT simulations were run with position restraints
on aromatic ring carbon atoms. Simulated X-ray diffraction patterns 
generated from each configuration establishes a difference between the two
stacking modes. In each pattern, a faint ring is present at a distance of
$\approx$ 1.5 \angstrom \textsuperscript{-1} which is commonly identified
as the result of the average packing distance between alkane chains. 
The parallel displaced configuration contains two lines of high intensity.
The lines have the highest intensity where they intersect the alkane chain region
due to constructive interference between the two features. The lines are located 
at a qz value of 0.76 \angstrom \textsuperscript{-1}, half the qz value corresponding
to layer stacking. This is significant because the same relative spacing between 
reflections is present in the expermental WAXS pattern between the pi-pi stacking
reflections at qz = 1.7 \angstrom \textsuperscript{-1} and the reflection attributed
to 2_1 helical ordering at qz = 0.85 \angstrom \textsuperscript{-1}. As the 
simulation is progressed, the full line begins to fade and the high intensity
persists only at the intersection with the alkane chain ring. Most significantly, 
the line is no longer present at r = 0. It is possible

generated for structures created in the parallel displaced configuration.
In the past, the spots have been attributed to the tilt angle of the 
alkane chains. Theoretically the angle is the same as that made between 
the spots and the x-axis. However, we achieved the same pattern with 
a calculated average tilt angle of 0 $\pm$ 9 degrees. % GET THE RIGHT NUMBER !!!!!
